---
title: "Project"
format: html
editor: visual
---

## File description:

The India Housing Prices Data set contains 2.5 lakh rows and 23 columns, offering detailed insights into housing market trends across various Indian states. It includes attributes related to property types, pricing, location, and amenities, making it suitable for analysis ranging from basic descriptive statistics to advanced machine learning applications.

```{r}
dt = read.csv(file = "D:/MTTS STDSMLAI/Project/india_housing_prices.csv", 
              header = TRUE)
head(dt)
```

```{r}
dim(dt)
```

```{r}
colnames(dt)
```

## Column Description

Some understanding from our Data set

-   **ID**: Different rows having different Integer values

-   **State**: Name of States of India ( character )

-   **City**: Name of Cities ( character )

-   **Locality**: Name of Localities ( character )

-   **Property_Type**: 3 types of property. ( Apartment, Independent House, Villa )

-   **BHK**: 5 varieties are there. ( 1,2,3,4,5)

-   **Size_in_sqFt**: Plot size in Sqft. ( integer )

-   **Price_in_Lakhs**: House price in Lakhs ( Double )

-   **Price_per_SqFt**: House price per Sqft. ( Double )

    **Price_in_Lakhs = Size_in_SqFt × Price_per_SqFt** 

-   **Year_Built**: Year of built. ( integer )

-   **Furnished_Status**: Furnished Status ( Furnished, Unfurnished, Semi-furnished )

-   **Floor_No**: Floor No ( Integer )

-   **Total_Floors**: Total floor in the house ( Integer )

-   **Age_of_Property**: Age of property ( Integer )

-   **Nearby_Schools**: No. of nearby schools. ( Integer )

-   **Nearby_Hospitals**: No. of nearby hospital. ( Integer )

-   **Public_Transport_Accessibility**: Chance of getting Public Transportation (High, Low, Medium )

-   **Parking_Space**: Parking Space present or not ( Yes, No )

-   **Security**: ( Yes, No )

-   **Amenities**: Amenities like: Playground, Gym, Pool, etc.

-   **Facing**: House Facing in which Direction ( East, West, South, North )

-   **Owner_Type**: Type of owner ( Owner, Builder, Broker )

-   **Availability_Status**: Status of availability ( Ready_to_move, Under_construction )

```{r}
typeof(dt$Availability_Status)
length(unique(dt$Availability_Status))
```

```{r}
summary(dt$Size_in_SqFt)
```

```{r}
boxplot(dt$Size_in_SqFt,horizontal = TRUE )
```

```{r}
summary(dt$Price_in_Lakhs)
val = dt$Price_in_Lakhs/10
summary(val)
boxplot(dt$Price_in_Lakhs)
```

```{r}
summary(dt$Price_per_SqFt)
boxplot(dt$Price_per_SqFt)
plot( dt$Price_per_SqFt)
```
